\let\textcircled=\pgftextcircled
\chapter{Conclusions}
\label{chap:conclusions}

\initial{O}verall, the project has reached all its main goals. The sentiment analysis and topic modelling models have been successfully implemented, tested and validated and packed into an application which could be run from a command line. Depending on the further requirements, the output of the program could be presented in a number of ways such as email or push notifications, as well as a simple command line output. 

\par The project could be continued and a lot more Natural Language techniques could be applied to the models. The main constraint of this project has been time, and a lot of extremely interesting topics have only been touched slightly, and a lot more time and other resources could be spent on this project. For example, noun phrase extraction has been tried as a part of the sentiment analysis, and it would be very useful to have it implemented. However, in the scope of this project only allowed a library (NLTK) method to be used for noun phrase extraction, and it proved not to be very successful - each noun extraction would take almost 3 seconds, and a lot of noun phrases would not be detected. It wold be very interesting to implement a fast and light noun phrase extractor, however, it would require a lot more time. 

If this project is ever continued, the person working on it should take all the points above into consideration. Despite the fact that the direction of the project had to be changed slightly, I hope that, with all the effort that has been put into this project, it will prove useful and contribute to a very interesting project and, hopefully, still move the Falkirk Council's project closer to the goal. 

It was incredibly interesting to work on this project, I learnt an immense amount of information, realised what the most interesting field of Computer Science is (for me, at least), received a lot of experience in Natural Language Processing, Machine Learning, working with APIs and so much more, and, generally, had an amazing time working on it. I also consider everything I have learnt throughout working on this project to be my largest achievement. 